Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-22 ICML-submission/introduction.tex
Removed an extra dot

The performance of the learner is measured by its cumulative number of
mistakes $\sum_{t=1}^T z_t = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$,
where $\one$ denotes the indicator function..

>>>>

The performance of the learner is measured by its cumulative number of
mistakes $\sum_{t=1}^T z_t = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$,
where $\one$ denotes the indicator function.
